More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-02-16 2016-Weak-FH-Bisim/WeakBisim.tex

Lemma \ref{lem-compose} is combining an open transition of $P$ with
an open transition of $Q$, and building a corresponding transition of
$P[Q]_{j_0}$, assembling their predicates.
\TODO{LUDO: REPROVE}
\begin{lemma}[Open transition composition]\label{lem-compose} 
	Suppose $j_0\in J$ and:\\[-2ex]
\begin{mathpar}
%\[
P\models{\inferrule*[myfraction=\reddottedrule]
	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I},
		\{\xrightarrow{b_j}_j\}^{j\in J}, \\\\
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {v}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\text{~and~}
%\[
Q\models{\inferrule*[myfraction=\reddottedrule]
	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I_Q},
		\{\xrightarrow{b_j}_j\}^{j\in J_Q},\\\\
		 \Pred\,',  
		\Post\,'}
	{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
		\ostate{s_i'^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\inferrule*[myfraction=\reddottedrule]
		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I \uplus I_Q},
			\{\xrightarrow{b_j}_j\}^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\subst{b_{j_0}\leftarrow v_Q}\land\Pred\,',  
			\Post\uplus \Post\,'}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {v}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\begin{small}

@@

       Consider each premise of the open transition (constructed by TR2 in 
Definition~\ref{def:operationalSemantics}). 
We know each premise is true for $P$ and try to prove the equivalent premise for 
$P[Q]_{j_0}$ (using the open transition of $Q$). 
$K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
$SV=clone(\alpha_j^{j\in I_k\uplus\{j_0\}\uplus 
	J_k})$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. All sub-pNets can be 
reduced:\\[-2ex]%\footnote{again we skip arguments related to renaming of fresh 
%variables}:
\[\forall m\in I_k\cup \{j_0\}.
\pNet_m \models
\inferrule*[myfraction=\reddottedrule]
{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I'_m},
	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
{\ostate{s_{i}^{i \in L_k}} \OTarrow {v_m}
	\ostate{s_{i}'^{\, i \in L_k}}}\]
the last sub-pNet is the one filled by $Q$ which offers an open transition by hypothesis.
Let $I'=\biguplus_{m\in I_k} I_m \uplus I_Q = I \uplus I_Q$ and $J'= \biguplus_{m\in I_k} 
J_m \uplus J_Q \uplus J_k = J\setminus\{j_0\}\uplus J_Q$. The predicate for the open 
transition is: $\Pred\,''=\bigwedge_{m\in I_k}\Pred_m \land \Pred\,'
\land \Pred(SV,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),b_j^{j\in J_k},v)$. By definition 
$\Pred(SV,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),b_j^{j\in J_k},v)\Leftrightarrow
	\forall i\in I_k.\, a_i=\alpha_i\land \forall j \in J_k.\, b_j=\alpha_j \land 
	\alpha'_k=v\land v_Q=\alpha_{j_0}$, finally $\Pred\,''=\Pred\subst{b_{j_0}\leftarrow 
	v_Q} \land \Pred\,'$. The post-condition gathers the post-conditions related to all 
	the leaves. Finally, the composed open transition can be
        built. \qed
        \end{proof}
\end{small}

>>>>

Lemma \ref{lem-compose} is combining an open transition of $P$ with
an open transition of $Q$, and building a corresponding transition of
$P[Q]_{j_0}$, assembling their predicates.

\begin{lemma}[Open transition composition]\label{lem-compose} 
	Suppose $j_0\in J$ and:\\[-2ex]
\begin{mathpar}
%\[
P\models{\inferrule*[myfraction=\reddottedrule]
	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I},
		\{\xrightarrow{b_j}_j\}^{j\in J}, \\\\
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {v}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\text{~and~}
%\[
Q\models{\inferrule*[myfraction=\reddottedrule]
	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I_Q},
		\{\xrightarrow{b_j}_j\}^{j\in J_Q},\\\\
		 \Pred\,',  
		\Post\,'}
	{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
		\ostate{s_i'^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\inferrule*[myfraction=\reddottedrule]
		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I \uplus I_Q},
			\{\xrightarrow{b_j}_j\}^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\subst{b_{j_0}\leftarrow v_Q}\land\Pred\,',  
			\Post\uplus \Post\,'}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {v}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\begin{small}

@@

       Consider each premise of the open transition (constructed by Tr2 in 
Definition~\ref{def:operationalSemantics}). 
We know each premise is true for $P$ and try to prove the equivalent premise for 
$P[Q]_{j_0}$ (using the open transition of $Q$). 
$K$ and the synchronisation vector are unchanged ($j_0$ is now in the set of sub-pNets); 
$SV_k=\alpha_j^{j\in I\uplus\{j_0\}\uplus 
	J} \!\to\! 
    \alpha' |e_b$. $\Leaves(P[Q]_{j_0})=\Leaves(P)\uplus \Leaves(Q)$. $I$ and $J$ are the 
    set of leaves and holes of $P$, $I'$ and $J'$ are the sets of moving leaves and holes 
    in the reduction of $P$. All sub-pNets of 
    must
    be 
reduced:\\[-2ex]%\footnote{again we skip arguments related to renaming of fresh 
%variables}:
\[\forall m\!\!\in\!\! I\cup \{j_0\}. 	
    {\left(\begin{array}{l}
	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
		{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
\end{array}\right)}\]
the sub-pNet at position $j_0$ is the one filled by $Q$ which offers an open transition 
by hypothesis.
Let $I''=\biguplus_{m\in I} I'_m \uplus I_Q = I' \uplus I_Q$ and $J''= \biguplus_{m\in I} 
J_m \uplus J_Q \uplus J = J'\setminus\{j_0\}\uplus J_Q$. The predicate for the open 
transition is: $\Pred\,''=\bigwedge_{m\in I}\Pred_m \land \Pred\,'
\land \Pred(SV_k,a_i^{i\in I_k}\uplus(j_0\mapsto v_Q),b_j^{j\in J},v)$. By definition 
$\Pred(SV_k,a_i^{i\in I}\uplus(j_0\mapsto v_Q),b_j^{j\in J},v)\Leftrightarrow
	\forall i\in I.\, a_i=\alpha_i\land \forall j \in J.\, b_j=\alpha_j \land 
	\alpha'_k=v\land v_Q=\alpha_{j_0}\land e_b$, finally 
	$\Pred\,''=\Pred\subst{b_{j_0}\leftarrow 
	v_Q} \land \Pred\,'$. The post-condition gathers the post-conditions related to all 
	the leaves. Finally, the composed open transition can be
        built. \qed
        \end{proof}
\end{small}
